---
title: "F1_OMR_new_structure"
author: "MD IMRAN NOOR"
date: "2023-11-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
setwd("J:/PhD/Semester 1.2/4. Fall Lab 2023/OMR")
library(car)
library(cowplot)
library(Matrix)
library(lme4)
library(emmeans)
library(multcomp)
library(afex)
library(tidyverse)
```

```{r}
omrf1 <- read.csv("omrf1_long.csv")
omrf1$treatment <- as.factor(omrf1$treatment)
omrf1$sex <- as.factor(omrf1$sex)
omrf1$subject <- as.factor(omrf1$subject)
omrf1$frequency <- as.factor(omrf1$frequency)
glimpse(omrf1)
```
###############################################################
#Model 1 = m1, where all but positive responses are 0, positive responses are 1
#All but positive responses are 0, positive responses are 1, m1
```{r}
#Mixed model
modelf1m1 <- glmer(responsem1 ~ treatment * sex + 
                     (frequency|subject), data = omrf1, family = binomial(link = "logit"))
summary(modelf1m1)
```
#All but positive responses are 0, positive responses are 1, m1
```{r}
#TukeyHSD on treatment
tukey_resultsf1m1treatment <- (glht(modelf1m1, mcp(treatment="Tukey")))
summary(tukey_resultsf1m1treatment)
```
#All but positive responses are 0, positive responses are 1, m1
```{r}
#TukeyHSD on sex
tukey_resultsf1m1sex <- (glht(modelf1m1, mcp(sex="Tukey")))
summary(tukey_resultsf1m1sex)
```
###############################################################
#Model 2 = m2 where all but no response to 1, and no responses to to 0
#All but no response are 1, and no responses are 0, m2
```{r}
#Mixed model 
modelf1m2 <- glmer(responsem2 ~ treatment * sex + 
                     (frequency|subject), data = omrf1, family = binomial(link = "logit"))
summary(modelf1m2)
```
#All but no response are 1, and no responses are 0, m2
```{r}
#TukeyHSD on treatment
tukey_resultsf1m2treatment <- (glht(modelf1m2, mcp(treatment="Tukey")))
summary(tukey_resultsf1m2treatment)
```
#All but no response are 1, and no responses are 0, m2
```{r}
#TukeyHSD on sex
tukey_resultsf1m2sex <- (glht(modelf1m2, mcp(sex="Tukey")))
summary(tukey_resultsf1m2sex)
```
###############################################################
#Model 3 = m3, where all but negative response are 1 and negative response are 0,
#All but negative response are o 1 and negative response are 0, m3
```{r}
#Mixed model
modelf1m3 <- glmer(responsem3 ~ treatment * sex + 
                     (frequency|subject), data = omrf1, family = binomial(link = "logit"))
summary(modelf1m3)
```
#All but negative response are o 1 and negative response are 0, m3
```{r}
#TukeyHSD on treatment
tukey_resultsf1m3treatment <- (glht(modelf1m3, mcp(treatment="Tukey")))
summary(tukey_resultsf1m3treatment)
```
#All but negative response are o 1 and negative response are 0, m3
```{r}
#TukeyHSD on sex
tukey_resultsf1m3sex <- (glht(modelf1m3, mcp(sex="Tukey")))
summary(tukey_resultsf1m3sex)
```

